---
title: "Visualize Data"
author: "Storm Zierden"
format: gfm
execute: 
  echo: true
  eval: true
---
```{r}
#| label: setup
#| include: false
library(tidyverse)
```


<!-- If you get the error "Error in list2(na.rm = na.rm, ...) : object 'ffi_list2' not found" do the following in the Console run:  

    remove.packages("rlang")

Then Restart R to be safe. Then run:

    install.packages("rlang")

and again restart R to be safe. That should fix the problem (which is a package dependency issue).   -->


## Your Turn 0

Add a setup chunk that loads the tidyverse packages.


```{r}
#| label: mpg-data
head(mpg)
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}
#| label: scatterplot-graph
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ,
                           y = hwy))
```


## Your Turn 2

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
#| label: boxplot
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = displ,
                             y = hwy))
```


## Your Turn 3

Make a histogram of the `hwy` variable from `mpg`. Hint: do not supply a y variable.

```{r}
#| label: histogram
ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy))
```

## Your Turn 4

Use the help page for `geom_histogram` to make the bins 2 units wide.

```{r}
#| label: hstogram-bin-2
 ggplot(data = mpg) +
  geom_histogram(mapping = aes(x = hwy),
                               binwidth = 2)
```


## Your Turn 5

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
#| label: scatterplot-color
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, 
                           y = hwy,
                           color = class)) + labs(x = "Engine Size Displacement",
                                                  y = "Highway Mileage (mpg)",
                                                  color = "Class of Vehicle",
                                                  title = "The bigger the engine the les mileage we get on the highway") +
  theme_dark()

```

## Help Me

What do `facet_grid()` and `facet_wrap()` do? 
(run the code, interpret, convince your group)

```{r}
#| label: facet-graphs
# Makes a plot that the commands below will modify
q <- ggplot(mpg) + geom_point(aes(x = displ, y = hwy))

q + facet_grid(. ~ cyl) # creates individual graphs based upon engine size by creating more columns
q + facet_grid(drv ~ .) # creates individual graphs upon where the engine is located by creating more rows
q + facet_grid(drv ~ cyl) # creates individual graphs combing the engine size and locatioon data 
q + facet_wrap(~ class) # creates individual graphs upon the type of car
```


## Your Turn 6

Make a bar chart `class` colored by `class`. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}
#| label: barplot-color
ggplot(data = mpg) +
  geom_bar(aes(x = class, fill = class))
```

## Quiz

What will this code do?

```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point(aes(color = class)) +
  geom_smooth(color = "black",
              se = FALSE,
              method = "lm") +
  scale_color_viridis_d()
  
ggsave("example.jpg", width = 6, height = 4)
```


*It will add two geometry to one plot*

# Take aways

You can use this starter code template to make thousands of graphs with **ggplot2**.

```{r}
#| label: template
#| eval: false
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```